Photo-z for LSST: comparison of PDFs

### 2017-06-16 main.tex
Update on Overleaf.

@@

>>>>

\subsection{BPZ}\label{sec:BPZ}
\texttt{BPZ}\footnote{We use \texttt{BPZ v 1.99.3}, available at: \url{http://www.stsci.edu/~dcoe/BPZ/}} \citep[Bayesian Photometric-$z$, see][for details]{Benitez:00} is a template-based photo-$z$ code which compares the expected colors (C) calculated for a set of SED types/templates (T) to the actual observed colors to calculate the likelihood of observing colors $p(C|z,T)$ at each redshift for each type.  The code employs an empirically determined Bayesian prior in apparent magnitude ($m_0$) and SED-type.  Assuming that the SED-types are spanning and exclusive, we can determine the redshift posterior by marginalizing over all SED-types with a simple sum (Eq.~3 from \citet[]{Benitez:00}):
\begin{equation}
p(z|C,m_0)\,\propto\, \sum_{T}p(z,T|m_0)\,p(C|z,T)
\end{equation}
\noindent where the first term is the Bayesian prior and the second term is the traditional likelihood.  The prior is assumed to have the form: $p(z,T|m_0) = p(T|m_0)\,p(z|T,m_0)$that is, it parameterizes the prior as an evolving type fraction with apparent magnitude, combined with a prior on the expected redshift probability distribution as a function of both apparent magnitude and SED-type.\\

The template set used for the Buzzard dataset is the set of 100 SEDs described in Section~\ref{sec:buzztemplates}, and use the 129 Brown SEDs for the Galacticus dataset.  For both datasets, to keep the number of free parameters to a manageable level, the SEDs in the training set are sorted by rest-frame $u-g$ colour and split into three ``broad'' SED classes, equivalent to the \texttt{E}, \texttt{Sp} and \texttt{Im/SB} types in \citet[]{Benitez:00}.  We assume the same functional form for the Bayesian prios as used by \citet[]{Benitez:00}, and utilize the training-set galaxies with known SED-type, redshift, and apparent magnitude to determine the type fractions and the best fit for the 11 free parameters of the prior.  For photo-$z$ point estimate we use the \texttt{Z\_B} output parameter.  For the type-marginalized p(z) is generated by setting the parameter \texttt{PROBS\_LITE=TRUE}.

@@

\subsubsection{Templates}\label{sec:buzztemplates}
[Describe the templates here? Or describe them earlier?]

\subsection{Galacticus [ABC?]}\label{Galacticus}
